### 2016-10-21 experiments.tex
new exp and MUSEUM stuff

All mutants were produced using the C mutation tool written by Jamie Andrews \cite{mutant}, used in many previous experiments in mutation analysis and software testing.  Andrews' tool applies only four operators: statement deletion, conditional negation, operator replacement, and constant replacement, chosen as a small set that still produces good results for C code.  The tool was chosen to keep the number of mutants as small as possible to control the cost of mutation analysis.  Coverage was analyzed with gcov.   All experiments were performed on a MacBook Pro with 16GB RAM and dual-core 3.1GHz Intel Core i7 (not using the second core); GCC executed on a VirtualBox-hosted Ubuntu 11.04.  For GCC, some test cases from the 2013 PLDI paper no longer failed, presumably due to unknown differences in execution environment, OS, or memory layout. Discarding these reduced the set of test cases from 1,275 to 1,117 and the number of distinct faults to 27 rather than 35.  For SpiderMonkey, all 1,749 test cases from the PLDI 2013 data failed in the new environment, representing 28 distinct faults.

@@

In order to check whether the improvement is statistically reliable for SpiderMonkey 1.6 faults, we sliced the PLDI 13 tests into 20 randomly selected distinct subsets.  The repair metric had a mean APFD for these subsets (about 90 tests, with a mean of just over 10 distinct faults) 2.85\% better than the mean APFD for the PLDI 13 metric, and the result was statistically significant ($p < 0.05$ by Wilcoxon test).

@@

@@

Mutation analysis is not cheap.  The experiments in this paper were run over a long period of time.  However, there are numerous ways to reduce costs.  First, the primary cost is compiling the mutated versions of the SUT.  Running each test case under each mutated version of the compiler is cheap: each execution requires around 0.05 seconds for SpiderMonkey, and 0.12 seconds for GCC, on average.  These executions can obviously be performed in parallel, on low-cost virtual machines in the cloud.  The cost is further reduced by a few more facts: most failures do not cover most mutants, and vice versa, so the total number of repair checks needed is far less than the product of mutants and failures.  The practical approach to fuzzer taming for a large, ongoing project is likely to maintain a set of ``hot'' pre-compiled mutants.  These can be pruned at will by running them on passing test cases, and removing mutants that fail on any test case.  Keeping hot mutants for a heavily modified program could be costly (since each mutant must be recompiled, if not re-tested, for each modification to the code), but for stable releases this is a simple approach to keep costs low.

>>>>

All mutants were produced using the C mutation tool written by Jamie Andrews \cite{mutant}, used in many previous experiments in mutation analysis and software testing.  Andrews' tool applies only four operators: statement deletion, conditional negation, operator replacement, and constant replacement, chosen as a small set that still produces good results for C code.  Coverage was analyzed with gcov.   All experiments were performed on a MacBook Pro with 16GB RAM and dual-core 3.1GHz Intel Core i7 (not using the second core); GCC executed on a VirtualBox-hosted Ubuntu 11.04.  For GCC, some test cases from the 2013 PLDI paper no longer failed, presumably due to unknown differences in execution environment, OS, or memory layout. Discarding these reduced the set of test cases from 1,275 to 1,117 and the number of distinct faults to 27 rather than 35.  For SpiderMonkey, all 1,749 test cases from the PLDI 2013 data failed in the new environment, representing 28 distinct faults.

@@

@@

In order to check whether the improvement is statistically reliable for SpiderMonkey 1.6 faults, we sliced the PLDI 13 tests into 20 randomly selected equal-sized (as much as possible) distinct subsets.  The repair metric had a mean APFD (89.23\%) for these subsets (about 90 tests, with a mean of just over 10 distinct faults) 2.85\% better than the mean APFD for the PLDI 13 metric (86.76\%), and the result was statistically significant ($p < 0.05$ by Wilcoxon test).   Median repair APFD was 90.05\%, vs. 84.75\% for PLDI 13's best metric.

@@

Mutation analysis is not cheap.  The experiments in this paper were run over a long period of time.  However, there are numerous ways to reduce costs.  First, the primary cost is compiling the mutated versions of the SUT.  Running each test case under each mutated version of the compiler is cheap: each execution requires around 0.05 seconds for SpiderMonkey, and 0.12 seconds for GCC, on average.  These executions can obviously be performed in parallel, on low-cost virtual machines in the cloud.  The cost is further reduced by a few more facts: most failures do not cover most mutants, and vice versa, so the total number of repair checks needed is far less than the product of mutants and failures.  The practical approach to fuzzer taming for a large, ongoing project is likely to maintain a set of ``hot'' pre-compiled mutants.  These can be pruned at will by running them on passing test cases, and removing mutants that fail on any test case.  
\begin{comment}
Keeping hot mutants for a heavily modified program could be costly (since each mutant must be recompiled, if not re-tested, for each modification to the code), but for stable releases this is a simple approach to keep costs low.
\end{comment}
